### 2021-11-25 input/proposal.tex
meow meow

\begin{definition}[\label{def:fd}\underline{F}orwarding of
    \underline{s}taleness (FS)]
  %
  To \NAMEB staleness, a \process $x$ delivers and forwards a received
  staleness notification if it is not yet delivered and targets its
  best delivered message: $\delta_s \in R_x \setminus D_x \wedge
  \alpha_s = \min D_x \TODO{\implies} d_x(\delta_s) \wedge
  f_x(\delta_s)$.
\end{definition}

@@

\begin{lemma}[\label{def:detection}\underline{D}etector existence (D)]
  Assuming a chain of \processes $[x,\ldots, z]$ that delivered a
  message $\alpha_x$ with $\alpha_x = \min D_z$, when $x$ deletes its
  partition, either every \process of this chain eventually delivers
  $\delta_x$, or a \process along the chain detects the blocking of
  the staleness notification $\delta_s$.
\end{lemma}

\begin{proof}
  Assuming a chain of \processes $[x, x_2, \ldots, y]$ such that
  $\alpha_x \min D$

>>>>

\begin{definition}[\label{def:fs}\underline{F}orwarding of
    \underline{s}taleness (FS)]
  %
  To \NAMEB staleness, a \process $x$ delivers and forwards a received
  staleness notification if it is not yet delivered and targets its
  best delivered message: $\delta_s \in R_x \setminus D_x \wedge
  \alpha_s = \min D_x \TODO{\implies} d_x(\delta_s) \wedge
  f_x(\delta_s)$.
\end{definition}

@@

\begin{lemma}[\label{def:detection}\underline{D}etector existence (D)]
  Assuming a chain of delivery of $\alpha_x$ from \Process~$x$ to
  \Process~$z$ with $\alpha_x = \min D_z$, if $x$ broadcasts a
  staleness notification $\delta_x$, either $z$ eventually delivers
  it, or a \process of the delivery chain $[x,\ldots, z]$ eventually
  detects its blocking.
  % $b_p(\delta_x) \implies d_q(x) U Detect[X]$ ??? 
\end{lemma}

\begin{proof}
  %% knowing that b_p delta is sufficient to say that processes will
  %% receive delta or detect blocking
  (A) Assuming a chain of delivery $C = [x, \ldots, z]$ of $\alpha_x$ with
  $\forall p \in C: \alpha_x = \min D_p$, and assuming
  $d_x(\delta_x)$, then with forwarding of staleness
  (Definition~\ref{def:fs}), $f_{C[k]}(\delta_x) \implies \eventually
  d_{C[k+1]}(\delta_x)$ except if $\delta_x \in D_{C[k+1]}$ which
  means that $C[k+1]$ already delivered and forwarded $\delta_x$
  following another such a chain of delivery. Therefore, $z$
  eventually receives, hence delivers $\delta_x$.

  \noindent Assuming a chain of delivery $C = [x, \ldots, z]$ of
  $\alpha_x$ with $\alpha_x = \min D_z$, and assuming $d_x(\delta_x)$,
  then by (A), the staleness notification reaches a \process $y\in C$

  every \process eventually deliver and forward $\delta_x$ either
  following the same chain, except if $\alpha_x$ is already stale
  which

  $z$ does not receive, hence deliver $\delta_x$ when a \process $y$
  between $x$ and $z$ stops forwarding $\delta_x$ because it delivered
  another message $\alpha_s$ with $\alpha_s < \alpha_x$.

  Assuming a chain of \processes $[x, x_2, \ldots, y]$ such that
  $\alpha_x \min D$
